---
title: "Practical Maching Learning Course Project"
output: html_document
---   

### Background
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, our goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways.  

### Load the Data
The training data for this project are available here: [https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv]

The test data are available here: [https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv]

After downloading the data, we read them into R:


```{r}
training <- read.csv("C:/Users/qiushan/Downloads/pml-training.csv", na.strings=c("NA","#DIV/0!", ""))
testing <- read.csv("C:/Users/qiushan/Downloads/pml-testing.csv", na.strings=c("NA","#DIV/0!", ""))
``` 

### Data Cleaning

Upon inspection of the data, we found that the first 7 column of the dataset are not related to the outcome, so we take them off the sets. We also take off the columns that have NA values to simplify our model building

```{r}
training1 <- training[,-(1:7)]
training2<-training1[, colSums(is.na(training1))==0]
testing1<-testing[,-(1:7)]
testing2<-testing1[, colSums(is.na(testing1))==0]
```

###Picking the Models   
We partition the tidy training set into a 70% subtraining set and 30% subtesting set and fit the data with the decision tree and random forest models. Here are the results:

```{r}
library(caret)
set.seed(1234)


inTrain <- createDataPartition(y=training2$classe, p=0.7, list=FALSE)
subTraining <- training2[inTrain, ]
subTesting <- training2[-inTrain, ]
```

We try the decision tree first and check out the confusionMatrix

```{r}
library(rpart)
modelrpart<-rpart(classe~., data=subTraining, method="class")
predictionrpart <-predict(modelrpart,subTesting, type = "class")
confusionMatrix(predictionrpart, subTesting$classe)
```
Next we use the Random Forest and look at the confustionMatrix again
```{r}
library(randomForest)
modelrandomForest<-randomForest(classe~., data=subTraining, method="class")
predictionrandomForest <-predict(modelrandomForest,subTesting, type = "class")
confusionMatrix(predictionrandomForest, subTesting$classe)
```

From the result, we pick the RandomForest to as the prediction model. 

